Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2024-03-25 revisions.qmd

---
title: "Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report"
author: "C. B. Smith and E. H. Hagen"
date: "`r Sys.Date()`"
output:
 bookdown::html_document2:
   number_sections: false
 bookdown::pdf_document2:
   number_sections: false
   latex_engine: xelatex
 bookdown::word_document2:
   number_sections: false
csl: apa.csl
bibliography: regrep.bib
crossref:
  custom: 
    - kind: float # crossreferenceable elements with captions are `float`
      prefix: Supplementary Figure # used as the prefix for reference in output ("In Figure 1, ..")
      name: Supplementary Figure # used as the prefix for captions ("Figure 1: ..")
      ref-type: sfig # used as the prefix for the reference identifier ("In @fig-1, ...")
---

@@

con <- designsG$d.design.adults %>%
  tbl_svysummary(
    by = sex,
    include = c(
      age_first_sex,
      sex_partners,
      sex_partners_year,
      strength,
      age,
      bmi,
      height,
      weight,
      whitebloodcell,
      hemoglobin,
      testosterone, 
      chronic_disease_score,
      physical_disease_count,
      depression,
      avgcalories, 
      avgprotein,
      foodinsecurity_adult, 
      tot_MET
    ),
    label  = list(
      age_first_sex = "Age at first sex (years)",
      sex_partners = "Lifetime number of sexual partners",
      sex_partners_year = "Past year number of sexual partners",
      strength = "Combined Grip Strength (kg)",
      age = "Age (Years)",
      bmi = "Body mass index (kg/m^2)",
      height = "Height (cm)",
      weight = "Weight (kg)",
      whitebloodcell = "White blood cell count (1000 cells/µL)",
      hemoglobin = "Hemoglobin (g/dL)",
      testosterone = "Testosterone (ng/dL)",
      chronic_disease_score = "Chronic Disease Score (0-6)",
      physical_disease_count = "Disease Impairment Score (0-5)",
      depression = "Depression Score (0-27)",
      avgcalories = "Dietary energy intake (kcals)", 
      avgprotein = "Dietary protein intake (grams)",
      foodinsecurity_adult = "Food Insecurity Rating (1-4)", 
      tot_MET = "Total MET"
    ),
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n_unweighted} ({p}%)"),
    digits = all_continuous() ~ 2,
    type = list(
      chronic_disease_score ~ "continuous",
      physical_disease_count ~ "continuous", 
      foodinsecurity_adult ~ "continuous"
    ),
    missing = "no"
  ) %>%
  modify_table_body(
    ~ .x %>%
      dplyr::mutate(ratio = getratio$table_body$ratio, digits = 2) %>%
      dplyr::mutate(n_male = getncon$table_body$stat_1, digits = 2) %>%
      dplyr::mutate(n_female = getncon$table_body$stat_2, digits = 2) %>%
      dplyr::relocate(n_male, .before = stat_1) %>%
      dplyr::relocate(n_female, .before = stat_2)
  )  %>%
  add_difference(test = everything() ~ "smd",
                 estimate_fun = purrr::partial(style_ratio, digits = 2)) %>%
  modify_column_hide(columns = ci) %>%
  modify_header(
    label = "**Variable**",
    ratio = "**Ratio**",
    n_male = "**N**",
    n_female = "**N**",
    stat_1 = "**Mean (SD)**",
    stat_2 = "**Mean (SD)**",
    estimate = "*d*"
  ) %>%
  modify_spanning_header(list(
    c("stat_1", "n_male") ~ "**Male**",
    c("stat_2", "n_female") ~ "**Female**",
    c("ratio", "estimate") ~ "**Sexual Dimorphism**"
  )) %>%
  modify_footnote(all_stat_cols() ~ "Weighted means and standard deviations shown for continuous variables, unweighted n (%) for categorical variables") %>%
  modify_caption("**Sex differences for participants ages 18-60 using population weights**") %>%
  bold_labels()

>>>>

---
title: "Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report"
author: "C. B. Smith and E. H. Hagen"
date: "`r Sys.Date()`"
output:
 bookdown::html_document2:
   number_sections: false
 bookdown::pdf_document2:
   number_sections: false
   latex_engine: xelatex
 bookdown::word_document2:
   number_sections: false
csl: apa.csl
bibliography: regrep.bib
crossref:
  custom:
    - kind: float
      reference-prefix: Figure S
      key: sfig
      space-before-numbering: false
---

@@

con <- designsG$d.design.adults %>%
  tbl_svysummary(
    by = sex,
    include = c(
      age_first_sex,
      sex_partners,
      sex_partners_year,
      strength,
      age,
      bmi,
      height,
      weight,
      whitebloodcell,
      hemoglobin,
      testosterone, 
      chronic_disease_score,
      physical_disease_count,
      depression,
      avgcalories, 
      avgprotein,
      foodinsecurity_adult, 
      tot_MET
    ),
    label  = list(
      age_first_sex = "Age at first sex (years)",
      sex_partners = "Lifetime number of sexual partners",
      sex_partners_year = "Past year number of sexual partners",
      strength = "Combined Grip Strength (kg)",
      age = "Age (Years)",
      bmi = "Body mass index (kg/m^2)",
      height = "Height (cm)",
      weight = "Weight (kg)",
      whitebloodcell = "White blood cell count (1000 cells/µL)",
      hemoglobin = "Hemoglobin (g/dL)",
      testosterone = "Testosterone (ng/dL)",
      chronic_disease_score = "Chronic Disease Score (0-6)",
      physical_disease_count = "Disease Impairment Score (0-5)",
      depression = "Depression Score (0-27)",
      avgcalories = "Dietary energy intake (kcals)", 
      avgprotein = "Dietary protein intake (grams)",
      foodinsecurity_adult = "Food Insecurity Rating (1-4)", 
      tot_MET = "Total MET"
    ),
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n_unweighted} ({p}%)"),
    digits = all_continuous() ~ 2,
    type = list(
      chronic_disease_score ~ "continuous",
      physical_disease_count ~ "continuous", 
      foodinsecurity_adult ~ "continuous"
    ),
    missing = "no"
  ) %>%
  modify_table_body(
    ~ .x %>%
      dplyr::mutate(ratio = getratio$table_body$ratio, digits = 2) %>%
      dplyr::mutate(n_male = getncon$table_body$stat_1, digits = 2) %>%
      dplyr::mutate(n_female = getncon$table_body$stat_2, digits = 2) %>%
      dplyr::relocate(n_male, .before = stat_1) %>%
      dplyr::relocate(n_female, .before = stat_2)
  )  %>%
  add_difference(test = everything() ~ "smd",
                 estimate_fun = list(all_continuous() ~ purrr::partial(style_ratio, digits = 2))) %>%
  modify_column_hide(columns = ci) %>%
  modify_header(
    label = "**Variable**",
    ratio = "**Ratio**",
    n_male = "**N**",
    n_female = "**N**",
    stat_1 = "**Mean (SD)**",
    stat_2 = "**Mean (SD)**",
    estimate = "*d*"
  ) %>%
  modify_spanning_header(list(
    c("stat_1", "n_male") ~ "**Male**",
    c("stat_2", "n_female") ~ "**Female**",
    c("ratio", "estimate") ~ "**Sexual Dimorphism**"
  )) %>%
  modify_footnote(all_stat_cols() ~ "Weighted means and standard deviations shown for continuous variables, unweighted n (%) for categorical variables") %>%
  modify_caption("**Sex differences for participants ages 18-60 using population weights**") %>%
  bold_labels()
